Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-11 Draft/shower.tex
added figures to the PS part; text to be added

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368) \pm 0.$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363) \pm 0.$  \\
        {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
        {\sc VBFNLO}  &  $X \pm 0.0003$  \\
        \hline
        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275) \pm 0.$  \\
        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $X  \pm 0.$  \\
        {\sc PHANTOM} &  $1.235  \pm 0.$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin}, see the text for details.}

{\bf MZ: MC uncertainties???}
\end{table}

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  \\
        \hline
        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 (1.368) \pm 0.$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 (1.363) \pm 0.$  \\
        {\sc POWHEG}  &  $1.3633 \pm 0.0004$  \\
        {\sc VBFNLO}  &  $X \pm 0.0003$  \\
        \hline
        {\sc MG5\_aMC}+{\sc Pythia8} (LO)&  $1.352 (1.275) \pm 0.$  \\
        {\sc MG5\_aMC}+{\sc Herwig++} (LO)&  $X  \pm 0.$  \\
        {\sc PHANTOM} &  $1.235  \pm 0.$  \\
    \end{tabular}
    \caption{\label{tab:wg1_NLOrates} Rates at NLO-QCD (LO-QCD) accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison, 
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. Numbers in parentheses for the {\sc MG5\_aMC} simulations
    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin}, see the text for details.}
{\bf MZ: MC uncertainties???}
\end{table}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/jetsexclusive.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/jetsexclusive.pdf}
\caption{Exclusive jet multiplicity from predictions matched to parton shower, at LO (left) or NLO (right) accuracy, compared with the fixed-NLO result
    computed with \sc{VBFNLO}}
\label{fig:PSnjet}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/m_jj.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/m_jj.pdf}
\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
\label{fig:PSmjj}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/Deltay_jj.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/Deltay_jj.pdf}
\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the rapidity separation of the two tagging jets.}
\label{fig:PSdyjj}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j1.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j1.pdf}
\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
\label{fig:PSpt1}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/pT_j2.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/pT_j2.pdf}
\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
\label{fig:PSpt2}
\end{figure*}

\begin{figure*}[hbt]
\centering
\includegraphics[width=0.47\textwidth]{figures/LOPS/y_j3.pdf}
\includegraphics[width=0.47\textwidth]{figures/NLOPS/y_j3.pdf}
\caption{Same as in Fig.~\protect\ref{fig:PSnjet}, for the invariant mass of the two tagging jets.}
\label{fig:PSy3}
\end{figure*}
